---
title: "Alcohol vs Seat choice"
author: "Paulo"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE} 
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The visual the plot shows quite a difference on the back row than the middle row and a big difference between the back row and the front row. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
``` 

Upon checking, the back row drinks 8.5 drinks a week. The front row dinks 1.78 drinks a week. The middle row drinks 3.33 drinks. Data shows that the they are not drinking the same amount. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The P value represents the chances of getting a result like we juts obtained if the null hypothesis is actually true. Since the result is so small, I am going to reject the null hypothesis. 

## Conclusions


